---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
options(width = 999)
```

# openbahn

`openbahn` provides functions to easily interact with the Timetable API, provided by the German railroad company _Deutsche Bahn_ (DB). At the moment, the API does only provide timetable data for the German long-distance traffic. The following API endpoints exist and are covered by `openbahn`:

- `location.name` to look up train stations
- `arrivalBoard` to retrieve arrival boards
- `departureBoard` to retrieve departure boards
- `journeyDetail` to retrieve detailed information for specific trains

To interact with the API, an API key is required.

## API Key

To get an API key, one has to email to the [DB Open-Data-Team](mailto:DBOpenData@deutschebahn.com) and request a key for the timetable or _Fahrplan_ API, respectively.

## Installation

You can install openbahn from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ottlngr/openbahn")
```

## Usage

First, `openbahn_auth()` can be used to store the API key in an environment variable all further `openbahn` functions will access:

```{r}
library(openbahn)
```

```{r,eval=FALSE}
openbahn_auth("YOUR_API_KEY_HERE")
```

`locationNameApi()` can be used to find a train station along with an internal ID and its coordinates:

```{r}
stations <- locationNameApi("Mainz Hbf")
stations
```

To retrieve arrival or departure boards, an `id` found in `stations` can be used. Furthermore, date and time the arrival or departure boards shall build on have to be provided:

```{r}
mainz_hbf <- stations$content$LocationList$StopLocation$id[1]

departures <- departureBoardApi(id = mainz_hbf, date = "2017-12-01", time = "12:00")
departures

arrivals <- arrivalBoardApi(id = mainz_hbf, date = "2017-12-01", time = "12:00")
arrivals
```

For the particular trains in the arrival or departures board one can retrieve detailed information using  `journeyDetailsApi()`. Therefor, the reference url of the desired train has to be looked up in the `JourneyDetailRef` data.frame:

```{r}
reference <- departures$content$DepartureBoard$Departure$JourneyDetailRef$ref[1]
details <- journeyDetailApi(reference_url = reference)
details
```

## References

For general information on the DB Timetable API visit http://data.deutschebahn.com/dataset/api-fahrplan (German). The data behind this API is licenced unter CC BY 4.0.

# Community Guidelines

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
